Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-07-04 ms.tex
explaining the difference in results with apertures on the subarray configu time series.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=0.48\columnwidth]{apertures_for_NRCN83-128-STRIPE-72.pdf}
\includegraphics[width=0.48\columnwidth]{apertures_for_NRCN83-256-STRIPE-72.pdf}
\includegraphics[width=.48\columnwidth]{subarray_config_tser_backsub_rect.pdf}
\caption{With rect backub.
\textcolor{red}{To do: understand better why the vertically offset box is better? Also, show the aperture as a separate figure.}}\label{fig:OTISRectBacksub}
\end{figure}

>>>>

\begin{figure}[!hbtp]
\centering
\includegraphics[width=0.48\columnwidth]{apertures_for_NRCN83-128-STRIPE-72.pdf}
\includegraphics[width=0.48\columnwidth]{apertures_for_NRCN83-256-STRIPE-72.pdf}
\includegraphics[width=.48\columnwidth]{subarray_config_tser_backsub_rect.pdf}
\caption{Subarray configuration test during OTIS. The position of the background subtraction box has a dramatic effect on the precision of the time series.
This is due to correlated 1/f noise along the horizontal fast-read direction.
If the background subtraction box is on an adjacent amplifier, it captures a very different 1/f noise behavior than if it is on a shared amplifier.
The amplifier boundary is shown as a vertical blue dashed line.
\textcolor{red}{To do: understand better why the vertically offset box is better? Also, show the aperture as a separate figure.}
\textcolor{blue}{Now I understand it as coming from which amplifier the background box is on.}}\label{fig:OTISRectBacksub}
\end{figure}
